Spatial Analysis of Russian Law Firm Names

### 2024-07-30 law-firms-names/Paper.Rmd
Add a subsection about naming strategies identification to methods, #5

>>>>

### 2.2.5. Naming strategies identification

Law firm names were clustered using the KMeans technique. A matrix of features for clustering was constructed from the name embeddings. As there were 256 items in each vector, the feature matrix had 256 columns. Target number of clusters was determined with elbow method and was ultimately set to 50, with the understanding that further manual processing of the clusterisation results would be necessary. Each name was assigned a cluster label between 1 and 50.

The resulting clusters were subsequently subjected to manual grouping. A random sample of 20 names was selected from each cluster. With 50 clusters and 20 sampled names allocated in each, the total size of the dataset for manual processing is 1, 000. The cluster samples were carefully examined, and a concise description was provided for each, e.g. “Names with the word “консалт/консалтинг” (consult/consulting)”. After this, the clusters were examined once more and assigned to one or more of the four groups: “Form”, “Law”, “Service”, “Misc”. The mapping of clusters and groups (e.g. cluster 1 — “Law”) was employed to link all the firm names to the appropriate groups. The concept of naming strategies was derived from the works of @Arora2015 and @BassolsiGardella2023. However, the specific groups differed from those used in their respective papers and were drawn from the data-driven analysis.

Each group except for the “Misc” category represents a specific naming strategy. The “Form” strategy encompasses names that are based on a word or words denoting a kind of business entity, including “company”, “firm”, “group”, “partnership”, “center”, “alliance”, and “corporation”. The “Law” strategy emphasises the firm's affiliation with the legal services market, employing terms such as “legal”, “juridical”, “lex”, “law”, “lawyer”. Names belonging to the “Service” strategy may indicate a particular service provided by a law firm (“advisor”, “consulting”, “protection”, “support”, “warrant”), describe the sectors of businesses the firm is primarily engaged with (“technology”, “development”, “house management”, “accounting”), or mention services in general. The “Misc” category is a catch-all group for names that do not clearly align with any other category.
